Topic modeling on EU and the USA research projects

### 2017-06-14 thesis_report/draft_thesis.tex
Related work: part (1/2)

@@

In this chapter we will present some basic theoretic background about topic
modeling. To deal with extensive text body, machine learning researchers have
developed topic modeling: a suite of methods that analyze the words of the
original text to discover the themes that run through the data and detect
hidden semantic structures by analyzing a corpus. By marking up the documents
using these topics and by using the resulting structure, the model can be used
for organization, finding similar documents, or any other similar tasks. A
topic is here defined as a probability distribution of words, meaning that
certain words are more likely within a certain topic. Since the topics emerge
from the analysis of the original texts, topic modeling algorithms do not
require any prior annotations or labeling of the documents.\cite{Blei:2012:PTM:2133806.2133826}

@@

LDA is a topic model that was first presented as a graphical model for topic
discovery by David Blei, Andrew Ng, and Michael I. Jordan in 2003. The basic
idea is that documents exhibit multiple topics. LDA is a generative statistical
model that allows sets of observations to be explained by unobserved groups
that explain why some parts of the data are similar. For example, if
observations are words collected into documents, it posits that each document
is a mixture of a small number of topics and that each word's occurrence is
attributable to one of the document's topics.\cite{Blei:2012:PTM:2133806.2133826}

>>>>

This chapter surveys previous work in topic modeling on scientific data. Topic
modeling algorithms provides a suite of algorithms to discover hidden thematic
structure in large collections of texts and can be adapted to many kinds of
data. These algorithms can be used to summarize, visualize and explore a
collection of documents. The papers listed below are applying a Latend Dirichlet
Allocation model in an interesting approach on their corpus.

D.Blei's research focuses on probabilistic topic models, Bayesian methods and
approximate posterior inference. In his work "Introduction to Probabilistic
Topic Models",\cite{Blei11introductionto} he describes the basic ideas behind
LDA and applies the model to articles from the journal "Science". The model
assumes that the topics are generated first, before the documents and that the
documents axhibit multiple topics, but each one of them exhibit those topics in
different proportion. In our implementation we also use the LDA model and we
follow a similar approach, since we don't use any previous information about the
subjects that run through our dataset and the documents are not labeled with
keywords or topics. The topic distributions arise by computing the hidden
structure that resembles the thematic structure of the collection.

The paper that mostly infuenced our work is "Finding Scientific Topics", by
T.Griffiths and M.Steyvers.\cite{griffiths_steyvers04} They investigated
abstract data from articles published in the Proceedings of the National Academy
of Sciences (PNAS) from 1991 to 2001 and compared research topics obtained from
topic modeling with existing categories. We also use the abstacts of the
projects as documents for the model. (to be continued)

@@

In this chapter we will present some basic theoretic background about topic
modeling. To deal with extensive text body, machine learning researchers have
developed topic modeling: a suite of methods that analyze the words of the
original text to discover the themes that run through the data and detect
hidden semantic structures by analyzing a corpus. By marking up the documents
using these topics and by using the resulting structure, the model can be used
for organization, finding similar documents, or any other similar tasks. A
topic is here defined as a probability distribution of words, meaning that
certain words are more likely within a certain topic. Since the topics emerge
from the analysis of the original texts, topic modeling algorithms do not
require any prior annotations or labeling of the documents.\cite{Blei11introductionto}

@@

LDA is a topic model that was first presented as a graphical model for topic
discovery by David Blei, Andrew Ng, and Michael I. Jordan in 2003. The basic
idea is that documents exhibit multiple topics. LDA is a generative statistical
model that allows sets of observations to be explained by unobserved groups
that explain why some parts of the data are similar. For example, if
observations are words collected into documents, it posits that each document
is a mixture of a small number of topics and that each word's occurrence is
attributable to one of the document's topics.\cite{Blei11introductionto}
